Multi sky-view\\ 3D aerosol distribution recovery

### 2013-07-31 article.tex
Modifications by Yoav

\title{Multi-view 3D Aerosol Distribution Recovery}

@@

% An infinitesimal volume contains aerosols. The extinction and
% scattering coefficients due to aerosols in this volume are,
% respectively
% \begin{equation}
%  \beta^{\rm aerosol}=\sigma^{\rm aerosol} n^{\rm aerosol}
%  \;\;,\;\;
%  \alpha^{\rm aerosol}=\varpi^{\rm aerosol} \beta^{\rm aerosol}
%  \;.
%  \label{eq:betaer}
%\end{equation}
%The infinitesimal volume contain also air molecules. Hence, the
% overall extinction and scattering coefficients in this small volume
% are, respectively
% \begin{equation}
%  \beta=\beta^{\rm air}+\beta^{\rm aerosol}
%  \;\;,\;\;
%  \alpha=\alpha^{\rm air}+\alpha^{\rm aerosol}
%  \;.
%  \label{eq:betair}
%\end{equation}

@@

\noindent {\bf Inverse Transform Sampling}: We use a Monte-Carlo (MC)
method as a tool for RT. MC considers scattering and attenuation as
random phenomena, that are sampled from their probability
distributions.  Sample random numbers that comply with any known
probability density function can be generated using inverse transform
sampling~\cite{devroye1986sample}. Let $u$ be a random number drawn
from a uniform distribution in the interval $[0,1]$. The number $u$
can be transformed into a random variable $X$, whose cumulative
distribution function (CDF) is $F(X)$. The transform is $X =
F^{-1}(u)$.

@@

\section{Methodology}
\label{sec:methodology}

Consider a set of ground-based wide-angle cameras
% ~\cite{Cossairt2011, Peleg01omnistereo:panoramic,
% Koppal:2011:WMS:2191740.2192152}
looking upwards (\cref{fig:groundgrid}). The set performs {\em
  integral imaging}~\cite{Hong2004} of the sky. Per viewpoint, the
view azimuth and elevation angles (relative to the zenith and north)
are encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
distinct fixed location ${\bm x}$, capturing raw image
$i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
a principle of estimating the 3D atmospheric aerosols distribution,
using such data. To show feasibility, we perform radiative transfer
using two different forward models, enabling cross-validation.  A
forward model takes as input the 3D aerosol distribution, and outputs
images as if captured at various viewpoints. One model uses Monte
Carlo (MC) methods (\cref{sec:monte-carlo-simul}): it is stochastic,
slow but naturally expresses multiple-scattering. Hence, this approach
simulates realistic scenes of arbitrary complexity.  The second model
uses the single-scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than MC, but
solves radiative transfer in an analytic, closed form. This form
enables simple inversion of the model, to estimate the underlying
atmosphere (\cref{sec:inverse-problem}).

@@

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$, $m$ or $q$. In a
\emph{single-scattering} model, any SR changes direction only once on
the way to a camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply. In this
model, radiative transfer has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$.
% Similarly, the single-scattering albdeos $\varpi^{\rm aerosol}$ in
% all voxels are stacked to vector $\vect{\varpi}$.
Using \cref{eq:alphabasic,eq:rayleighP}, the angular scattering
coefficients across the domain are expressed in vector form by
\begin{equation}
  \tilde{\vect{\alpha}}^{\rm air}_c =
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,
  \quad
  % \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
  % \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
  % g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \tilde{\vect{\alpha}}^{\rm aerosol}_c =
  \varpi^{\rm aerosol} \sigma^{\rm aerosol}
  {\bm n} \odot P^{\rm aerosol}_{\bm g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \label{eq:alpha_matrix}
\end{equation}
% The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter
% of the phase function, in all voxels. This notation indicates a
% parametric phase function as in \cref{eq:aerosol_scatter}.
Here the operator $\odot$ denotes the Hadamard (element-wise) product.

@@

A camera pixel collects light from a narrow cone in the
atmosphere. The cone contains or intersects some voxels, while being
oblivious to all the rest.
Overall, light power captured at a pixel is a weighted sum of the
power $p_c(k)$ from all voxels.  This sum is formulated by a matrix
operation over ${\bm p}_c$:
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;,
  \label{eq:IcP}
\end{equation}
where ${\bm i}_c$ is the image, column-stacked to a vector $N_{\rm
  pix}$ long.  Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured
image is thus
% \begin{align}
%   {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \left\{
%     (\tilde{\vect{\alpha}}^{\rm air}_c + \tilde{\vect{\alpha}}^{\rm
%     aerosol}_c) \odot \exp\{-[\vect{\tau}_c^{\rm air} + {\bm D}_c
%     (\vect{\sigma} \odot {\bm n})]\} \right\}
%   \label{eq:bigIc}
% \end{align}
% We focus on situations where there is only a single type of aerosol
% over a scene. Hence, the three-element vector $[{\sigma}^{\rm
% aerosol},\varpi^{\rm aerosol},g]$ is uniform across the scene, but
% the density distribution ${\bm n}$ is variable. Then,
% \cref{eq:bigIc} degenerates to
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
    aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
    n} ] \odot \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
  {\bm D}_c{\bm n})] \Big\} .
  \label{eq:bigIA}
\end{align}

@@

\section{Monte Carlo RT}
\label{sec:monte-carlo-simul}

Monte Carlo (MC) methods enable rigorous modeling of photon
propagation in the atmosphere.  MC simulations can be made arbitrarily
accurate by increasing the number of launched photons. MC methods are
highly parallelizable. When applied to the RT problem, they enable
simulating multiple scattering and produce realistic results.

The MC simulations use the same atmospheric grid described in
\cref{sec:single-scatt-model}. We use backward MC, i.e. photons are
traced from the detector, camera, to their source, the Sun, in a
direction determined by the camera model, i.e. hemispherical
camera. The quality of the simulations is proportional to the number
of photons. To create the \cref{fig:simulation-results1}b, \num{10000}
photons were emitted from each pixel. The distance travelled by the
photon till its first scattering is determined by sampling from the
transmittance distribution using the inverse transform sampling
(\cref{sec:theor-backgr}).  The CDF of the optical depth
(transmittance) distribution is given by,
\begin{equation}
  \label{eq:1}
  F=\int_{0}^{\tau}\exp(-\tau')\derivsym{\tau'}=1-\exp(-\tau)
\end{equation}
Given a uniformly distributed random number $u$ a random optical depth
is given by
\begin{equation}
  \label{eq:2}
  t=F^{-1}(u)=-\ln(1-u)
\end{equation}
The actual distance travelled by the photon is calculated by
accumulating the discrete optical depths of each voxel along the
photon's path till the target optical path, drawn by \cref{eq:2}, is
reached.  If the scattering occurs outside the atmospheric grid, the
photon is dropped. If not, the voxel in which the scattering occurs is
calculated.  The type of scattering, either by air molecule or aerosol
particle, is determined randomly according to their relative densities
in the voxel.  The new direction of the photon is determined by
inverse sampling the phase function of the scattering particle:
Rayleigh, \cref{eq:rayleighP}, or Henyey-Greenstein,
\cref{eq:aerosol_scatter}.  Local Estimation~\cite{marshak20053d} is
used for calculating the amount of light reaching the sun at each
scattering.  This process is repeated till the photon escapes the
atmosphere grid or it reaches a predetermined number of scatterings.

@@

In this paper, we assume that the type of the aerosol above an area is
known~\cite{Martonchik2009}. Hence, we focus on estimating the density
distribution $\DistUnknown$.
At hand, we have $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased
as optimization of an objective function that fits the image-formation
model to the measured photographs, under constraints. Let $\DistSet$
be the set of all legitimate distributions, according to constraints.
Particularly, $\DistEstimated$ is non-negative, and it has limited spatial
support between the ground and the TOA. The optimization problem is,
\begin{equation}
  \label{eq:minobjectiveA}
  \DistEstimated =
  \argmin_{\DistUnknown \in \DistSet} \CostFunc{\DistUnknown}
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  \CostFunc{\DistUnknown}
  = \sum_{c=1}^{N_{\rm views}}
  \| \MaskSun \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
  + \eta \Psi({\bm n})
\end{equation}
where $\MaskSun$ is a map that masks the areas around the sun, which are
overwhelmingly bright. %and the horizon.
% These regions are prone to dominant multiple scattering.
In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term
that expresses some prior knowledge on the distribution, while $\eta$
is a regularization weight.  Since aerosol distributions are usually
fuzzy, it can be beneficial that regularization be a {\em smoothness
  term}, which penalizes energy in second order spatial derivatives
(3D Laplacian). Hence, we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D
\emph{Laplacian} operator.

We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \eta
  \transpose{\Laplacian}\Laplacian{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
viewpoint $c$) with variation of the aerosol density at voxel $k$,
i.e., $\partial i_c({\bm \Theta})/\partial{n(k)}$.

>>>>

\title{Multi sky-view\\ 3D aerosol distribution recovery}

@@

@@

\noindent {\bf Inverse Transform Sampling}: A tool for RT is Monte-Carlo (MC)
simulation. MC considers scattering and extinction as
random phenomena, that are sampled from their probability
distributions.  Sample random numbers that comply with any known
probability density function can be generated using inverse transform
sampling~\cite{devroye1986sample}. Let $u$ be a random number drawn
from a uniform distribution in the interval $[0,1]$. The number $u$
can be transformed into a random variable $X$, whose cumulative
distribution function (CDF) is $F(X)$. The transform is $X =
F^{-1}(u)$.

For example, consider a photon propagating in the atmosphere.
The photon has high probability of propagating as long as $t$ is high, 
and the probability diminishes as $t\rightarrow 0$. Thus Eq.~(\ref{eq:beer-lambert}) can be viewed as a probability density function, whose CDF is 
\begin{equation}
  \label{eq:Ftau}
  F(\tau)=\int_{0}^{\tau}\exp(-\tau')\derivsym{\tau'}=1-\exp(-\tau).
\end{equation}
Thus a photon propagates to a random optical depth 
\begin{equation}
  \label{eq:taurand}
  \tau^{\rm random}=F^{-1}(u)=-\ln(1-u).
\end{equation}
If the atmosphere is uniform, then from Eq.~(\ref{eq:tau}) the photon reaches a random distance
\begin{equation}
  \label{eq:lrand}
  l^{\rm random}= (\beta^{\rm aerosol}+\beta^{\rm air})^{-1} \tau^{\rm random}
                = -(\beta^{\rm aerosol}+\beta^{\rm air})^{-1}\ln(1-u),
\end{equation}
before interacting with a particle. If the number of photons launched is very high, their average number falls off in consistency with Eqs.~(\ref{eq:tau},\ref{eq:beer-lambert}). 
Analogous transforms generate scattering at random angles, according to the phase function.

@@

\section{3D recovery approach and its assessment}
\label{sec:methodology}

A set of ground-based wide-angle cameras
looks upwards (\cref{fig:groundgrid}), performing {\em
  integral imaging}~\cite{Hong2004} of the sky. Per viewpoint, the
view azimuth and elevation angles (relative to the zenith and north)
are encapsulated in vector ${\bm{\Theta}}$. Any camera $c$ is at a
distinct fixed location, capturing raw image
$i_c({\bm{\Theta}})$. This paper takes a first step of formulating
a principle for estimating the 3D atmospheric aerosols distribution,
using such data. To study the feasibility and cross validate it, we perform RT
using two different forward models. A forward model takes as input a 3D aerosol distribution, and outputs images as if captured at various viewpoints. 
One model uses MC (\cref{sec:monte-carlo-simul}): it is stochastic,
slow but naturally expresses multiple-scattering. Hence, MC
rigorously simulates realistic scenes of arbitrary complexity. 
%MC simulations can be made arbitrarily accurate by increasing the number of launched %photons. MC methods are highly parallelizable. 
The second model uses the single-scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than MC, but
solves RT in an analytic, closed form. This form
enables simple inversion of the model, to estimate the underlying
aerosol distribution (\cref{sec:inverse-problem}).

@@

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$, $m$ or $q$. In a
\emph{single-scattering} model, any SR changes direction only once on
the way to a camera. This model is valid in atmospheres that are not
very dense: inside fog and clouds this model does not apply. In this
model, RT has three steps (\cref{fig:groundgrid}):
({\tt i}) Attenuation of a SR propagating from the top of the
atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel
$k$, towards a camera. ~({\tt iii}) Light attenuation on the LOS from
voxel $k$ to the camera.~~ Steps~{\tt i},{\tt iii} involve the optical
depth along the light path to and from voxel $k$, as analyzed in
\cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering
coefficient at voxel $k$, described in \cref{sec:scattering}.

@@

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$.
% Similarly, the single-scattering albdeos $\varpi^{\rm aerosol}$ in
% all voxels are stacked to vector $\vect{\varpi}$.
Using \cref{eq:alphabasic,eq:rayleighP}, the angular scattering
coefficients across the domain are expressed in vector form by
\begin{equation}
  \tilde{\vect{\alpha}}^{\rm air}_c =
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,
  \quad
  \tilde{\vect{\alpha}}^{\rm aerosol}_c =
  \varpi^{\rm aerosol} \sigma^{\rm aerosol}
  {\bm n} \odot P^{\rm aerosol}_{\bm g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \label{eq:alpha_matrix}
\end{equation}
Here the operator $\odot$ denotes the Hadamard (element-wise) product.

@@

A camera pixel collects light from a narrow cone in the
atmosphere. The cone contains or intersects some voxels, while being
oblivious to all the rest.
Overall, light power captured at a pixel is a weighted sum of the
power $p_c(k)$ from all voxels.  This sum is formulated by a matrix
operation over ${\bm p}_c$:
\begin{equation}
  {\bm i}_c= {\vect{\Pi}}_c{\bm p}_c
  \;\;,
  \label{eq:IcP}
\end{equation}
where ${\bm i}_c$ is the image, column-stacked to a vector $N_{\rm
  pix}$ long.  Combining \cref{eq:tautotal,eq:pc,eq:IcP}, the captured
image is thus
\begin{align}
  {\bm i}_c= L^{\rm TOA} {\vect{\Pi}}_c \Big\{
  [\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm aerosol}\sigma^{\rm
    aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm
    n} ] \odot \exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm aerosol}
  {\bm D}_c{\bm n})] \Big\} .
  \label{eq:bigIA}
\end{align}

@@

\section{Multiple-Scattering Forward Model by Monte Carlo}
\label{sec:monte-carlo-simul}

The MC simulations rely on the same grid as Sec.~\ref{sec:single-scatt-model}. We use backward MC: from a detector pixel, photons are `launched' via the camera lens; then the photons are traced back through the atmosphere. Photons that happen to be back-traced to the Sun are counted, per pixel. In this model, RT takes the following steps, per launched photon (\cref{fig:mcgrid}):\\
({\tt i}) Launch a photon from camera $c$ to direction ${\bm{\Theta}}$. This is the initial {\em ray}, denoted ${\cal R}_0$.\\
Per iteration $i$\\
({\tt ii}) Find the distance on ray ${\cal R}_{i}$ to which the photon propagates. To do this, Eq.~(\ref{eq:taurand}) yields $\tau^{\rm random}$. Then, Eq.~(\ref{eq:lrand}) generalizes to a non-uniform atmosphere: using Eq.~(\ref{eq:tau}), numerically seek $l^{\rm random}$ s.t.
\begin{align}
  \int_0^{l^{\rm random}}(\sigma^{\rm aerosol} n +\beta^{\rm air}) dl = \tau^{\rm random}
  \label{eq:MCextinct}
\end{align}
Distance $l^{\rm random}$ at ${\cal R}_{i}$ is 3D position ${\bf X}_{i}$.
If  ${\bf X}_{i}$ is outside the atmospheric grid, the photon is terminated. If, in addition,  ${\cal R}_{i}\parallel {\rm SR}$ , the photon is counted as contributing to the image pixel.\\
({\tt iii}) The type of particle (air molecule or aerosol) the photon interacts with at ${\bf X}_{i}$ is determined randomly according to their relative densities at the voxel containing ${\bf X}_{i}$.\\
({\tt iv}) If it is an aerosol, the photon is terminated with probability 
$1-\varpi^{\rm aerosol}$.\\
({\tt v}) The photon is scattered to a new direction, determined by inverse transform sampling, according to the phase function of the particle: \cref{eq:aerosol_scatter}
or~\cref{eq:rayleighP}. This yields a new {\em ray}, denoted ${\cal R}_{i+1}$, emanating from ${\bf X}_{i}$. The next iteration of propagation (denoted {\tt ii} above)  proceeds.\\
Local Estimation~\cite{marshak20053d} is used for calculating the amount of light back-traced to the sun at each scattering.

The quality of the simulations is proportional to the number of photons. To create the \cref{fig:simulation-results1}b, \num{10000}
photons were emitted from each pixel.

@@

In this paper, we assume that the type of the aerosol above an area is
known~\cite{Martonchik2009}. Hence, we focus on estimating the density
distribution $\DistUnknown$.
At hand, we have $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased
as optimization of an objective function that fits the image-formation
model to the measured photographs, under constraints. Let $\DistSet$
be the set of all legitimate distributions, according to constraints.
Particularly, $\DistUnknown$ is non-negative, and its spatial
support is bounded between the ground and the TOA. The optimization problem is
\begin{equation}
  \label{eq:minobjectiveA}
  \DistEstimated =
  \argmin_{\DistUnknown \in \DistSet} \CostFunc{\DistUnknown}
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  \CostFunc{\DistUnknown}
  = \sum_{c=1}^{N_{\rm views}}
  \left\| 
     \MaskSun[{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})]
  \right\|^2_2
  + \eta \Psi({\bm n})
\end{equation}
Here $\MaskSun$ masks the area around the sun, which in real-world photographs is indeed blocked. %and the horizon.
% These regions are prone to dominant multiple scattering.
In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term
that expresses some prior knowledge on the distribution, while $\eta$
is a regularization weight.

Since aerosol distributions are usually fuzzy, useful regularization is by a {\em smoothness term}, which penalizes energy in second order spatial derivatives
(3D Laplacian), $\| \nabla^2{\bm n}\|^2_2$. Regularization is not required when data is sufficient and reliable. As seen in Fig.~\ref{fig:groundgrid}, voxels at high altitude have good coverage by many cameras at multiple directions, while at low altitude voxels are mainly observed by local cameras. Hence, regularization can be weakened with altitude. We accomplished this weakening using a weight 
$w(k)=\exp\left[-h(k)/H^\mathrm{smooth}\right]$.  Overall we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| {\bf W} \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D Laplacian operator, and matrix
${\bf W}$ is diagonal, whose elements are $w(k)$.

We solve~\cref{eq:minobjectiveA} using standard optimization tools.
The gradient of $F$ with respect to ${\bm n}$ is
\begin{align}
  \Grad{{\bm n}} F = -2\sum_{c=1}^{N_{\rm views}}
  \transpose{\left[{\bm J}_{{\bm i}_c}({\bm n})\right]} [{\bm i}^{\rm
    measured}_c - {\bm i}_c({\bm n})] + 2 \eta
  \transpose{\Laplacian}\transpose{{\bf W}}{\bf W}\Laplacian{\bm n} \;.
  \label{eq:gradient1}
\end{align}
Here the matrix ${\bm J}_{{\bm i}_c}({\bm n})$ is the Jacobian of the
vector ${\bm i}_c$ with respect to ${\bm n}$.  Element $(\Theta,k)$ of
this matrix differentiates the intensity in pixel ${\bm \Theta}$ (in
viewpoint $c$) with variation of the aerosol density at voxel $k$,
i.e., $\partial i_c({\bm \Theta})/\partial{n(k)}$.
